---
title: "Computation of fractal dimension"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
### Libraries
```{r}
library(Rdimtools) # for fractal dimension
library(tools)
```

### Load the point clouds 

As an exemple to test the script, point clouds (txt files) are available on Zenodo:
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.8048122.svg)](https://doi.org/10.5281/zenodo.8048122)

Otherwise, to extract point clouds from 3D CAD models in the format STL, you can use a script on Python available at:

* Store all your point cloud at the format txt in a folder
* Export the name list of all the point clouds (txt files) stored in the folder

```{r}
setwd = "yourpath" # give the path where your store the 3D CAD models in .txt format
list = list.files(pattern = "\\.txt$")    

```

#### Create a loop to process the fractal dimension for each point clouds

* Create an empty object  `outputD` in which you'll concatenate fractal dimension

```{r}
output=NULL
for (i in 1:length(list)) {
  cat(paste0("--- ",Sys.time(),"processing_",list[i]," ---/n")) # to monitor the processing time for each table.
  Points=read.csv(list[i], sep=",")
  
  # computation of Dn
  outputD=est.boxcount(Points[,1:3], nlevel=100, cut = c(0.1,0.9)) # the result of the function est.boxcount
  D=outputD$estdim  # compile the estimation of the fractal dimension
  
  output=rbind(output,c(D))
  
}
```

#### Save the data

```{r}

row.names(output) = file_path_sans_ext(list[i]) # rename the row with the names of the 3D CAD models
write.csv2(output,"fractal_dimension.csv") 

```