---
title: "MFA for Complexity Target points "
output:
  html_document:
    df_print: paged
  pdf_document: default
  html_notebook: default
---

#### Libraries
```{r}
library(FactoMineR)
library(factoextra)
library(ggthemes)
library(ggplot2)
library(gridExtra)
library(vegan)
```

#### Load the data
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.8055070.svg)](https://doi.org/10.5281/zenodo.8055070)

```{r}

Indexes <- read.csv("df_complexity_indexes.csv", sep=",", row.names = 1, h=T)

```

### I. MFA

Once you have calculated the index on your 3D CAD models, you can bind the results to the table "Indexes". Once it's done you can calculate the CI for all the models including yours. You can then calculate the MFA with your models as additional individuals (argument: ind.sup). Your models will be plotted on the individual maps. 

```{r}

#MyModels <- read.csv("MyModels_df_complexity_indexes.csv", sep=",", row.names = 1, h=T)
#Indexes <- rbind(Indexes,MyModels)

res.mfa <- MFA(Indexes,
               # ind.sup = c()
               group = c(3,3),
               type = c("s","s"), 
               graph = F)

group_col <- c("#1c4587","#b45f06")

MFA_var <- fviz_mfa_var(res.mfa, palette = group_col, ggtheme = theme_few())


```

### II. HCPC

```{r}

res.hcpc <- HCPC(res.mfa, nb.clust = 4,graph = F, method = "ward")

my_palette <- alpha(c("#843734","#444444","#a38064","#086464"),0.5)

MFA_clust <- fviz_cluster(res.hcpc,
             cex = 1,
             palette = my_palette,              
             ggtheme = theme_few(),
             repel = TRUE,           
             show.clust.cent = T,     
             main = "Cluster map")

```

### III. Plot the MFA
```{r}
grid.arrange(MFA_clust, 
             MFA_var, 
             MCI, 
             nrow = 2, 
             layout_matrix = cbind(c(1,1),c(2,3)))
```
